A Rapid Feasibility Checking for Reconfiguration of Mismatched PV Arrays

### 2019-06-02 PVSC-46/Manuscript/PVSC_Manuscript.tex
Camera ready

%In final version, please replace the following two definitions
\newcommand{\michiko}{\textcolor{blue}}
%\newcommand{\michiko}{\textcolor{black}}

@@

\section{Introduction}\label{Sec1}
As fossil fuel depletion and environmental pollution become more serious, green and renewable energy has become necessary for a sustainable society and environment. 
Photovoltaic (PV) systems receive significant attention since the sun has unlimited energy and PV arrays can be easily scaled up. 
However, due to the nature of PV cell, which is a basic component of a PV array, PV arrays are sensitive to partial shading and PV cell damage. 
PV cells could not uniformly generate power when they experience different irradiances or some of them have physical defects, and such a mismatched condition might accelerate heating and aging of PV cells and cause further damaging. 
To prevent PV cells from damaging, bypass diodes are usually placed in PV arrays and they are turned on in mismatched conditions. 
However,  the operation of bypass diode will cause a number of PV cells to stop deliver power, %
\michiko{and it will hence result in a significant loss of power generation. }

@@

PV arrays are hierarchically constructed such that a group of PV cells form a PV module, a group of PV modules form a PV panel, and a group of PV panels form a PV array. 
Power generation of mismatched PV arrays can be recovered by reconfiguring connection of these components. 
Fig.\ref{compare} shows an example of power generations of a PV array with a partial shading. 
We distributed shading cells non-uniformly to a PV array with 3 $\times$  4 PV panels and applied power simulation. 
Before reconfiguration, \michiko{there are} multiple \michiko{peaks in a power - voltage curve with similar power levels,} while, after we reconfigured connection among PV panels, 
\michiko{some peaks exhibit much higher power levels than others and }
%MPPs has reduced and 
power generation increased by 35\%.

@@

Figure \ref{model} shows an example of a PV array. 
A PV array is a parallel connection of (PV) strings where a string is a series connection of PV panels. 
A PV panel is a series connection of PV modules, and a PV module is a parallel connection of a series of PV cells and a bypass diode. 
A typical commerical PV panel is composed of three PV modules each of which has 12-24 PV cells. 
A PV module can generate power for a given voltage according to its I-V characteristics as shown in Fig.\ref{fig:IV}(a - c). 
The I-V characteristics is affected by irradiance level and physical damage of PV cells. 
\michiko{Figure \ref{fig:IV}(a - c) also show} a typical degradation of a I-V characteristics where generated \michiko{currents are reduced} with some ratio while keeping the voltage range. 
When a PV panel has a partial shade, that is its PV modules have different irradiance levels and hence different I-V characteristics, the PV panels might have multiple peaks (maximum power points, MPPs) in power generation as shown in Fig.\ref{fig:IV}(d).

@@

Step 3 optimizes the number of active modules. 
In Step 3, if the number of active modules exceeds the required number $m$, redundant panels are canceled if exist. 
A panel is \textit{redundant} if the number of active modules is still $m$ or more even if the panel is canceled.  
Redundant panels are searched \michiko{for each loss level}. 
Starting with a loss level where the last panel is selected, we check the number of active modules $M_{p}(Q_{n})$ for each panel $p$ 
where $Q_{n}$ is a required current level for the current string.
Redundant panels are selected and canceled from panels with less number of $M_{p}(Q_{n})$ in the same loss level. 
If \michiko{the number of active modules} still exceeds $m$ after canceling,
the same procedure is applied to the previous loss level.
% we will go to the previous loss level and try to cancel panels.
This procedure is repeated until selecting an exactly $m$ active modules or checking all the loss levels.
\michiko{This step accurately finds redundant panels if exist in the following reason. Since the number of active modules in one panel is 0, 1, 2, or 3 and panels are selected from panels with less active modules in the same loss level, if the number of active modules exceed $m$, the surplus is 1 or 2. That means, the last selected panel has 2 or 3 active modules, and panels with 1 or 2 active modules have already selected if exist.}

@@

\michiko{To evaluate the proposed method, we prepared MPP informations of 100 mismatched PV arrays and applied our algorithm. We also applied an exhaustive searching algorithm for comparison.
MPP information is setup as follows for each PV array. 
Each PV array has 6 - 24  panels and the number of PV panels is randomly determined. 
Three current values are randomly assigned to the three modules in each panel from 3 - 8 current values, where the number of possible current values are also randomly determined for each PV array. 
The number of strings after reconfiguration is 3 - 6 and it is randomly determined for each PV array.}

@@

\michiko{Table~\ref{result_compare} shows the results of feasibility checking by the proposed algorithm and the exhaustive search.} 
%To evaluate the performance of  proposed algorithm, 
%we compare the result with exhaustive searching algorithm for 100 random shadow distributed PV arrays. For each PV array, 6 - 24 PV panels are connected into 3 - 6 PV strings. For each PV panel, it will has 3 - 8 working current values.
%The computational time required for finding optimal configuration and accuracy of feasibility judgment in the proposed algorithm and exhaustive search algorithm are compared in Table \ref{result_compare}. 
%As shown in Table \ref{result_compare},
% proposed algorithm achieved less computing time compare with exhaustive search algorithm and with high accuracy.  
%from 100 PV arrays, 486 configuration candidates are selected where each candidate is specified with a required current sequence for strings and the number of active modules per string.
Since the exhaustive search checks all the combinations of panel connections for each configuration candidate, it accurately identifies the feasibility of every configuration. % but that takes a lot of time.
\michiko{Though the exhaustive search identified total 327 feasible configurations, the proposed method identified 324 configurations and 3 configurations are misidentified. 
The proposed algorthm had a few false negative cases, but its rate was less than 1\%.
That is, it can correctly identify feasibility for most cases. 
Indeed, the proposed algorithm found at least one candidate configuration as feasible among 4 - 5 candidates for each PV arrays. }

>>>>

%In final version, please replace the following two definitions
\newcommand{\michiko}{\textcolor{black}}
%\newcommand{\michiko}{\textcolor{black}}
\newcommand{\zhao}{\textcolor{black}}

@@

\section{Introduction}\label{Sec1}
As fossil fuel depletion and environmental pollution become more serious, green and renewable energy has become necessary for a sustainable society and environment. 
Photovoltaic (PV) systems receive significant attention since the sun has unlimited energy and PV arrays can be easily scaled up. 
However, due to the nature of PV cell, which is a basic component of a PV array, PV arrays are sensitive to partial shading and PV cell damage. 
PV cells could not uniformly generate power when they experience different irradiances or some of them have physical defects, and such a mismatched condition might accelerate heating and aging of PV cells and cause further damaging.
To prevent PV cells from damaging, bypass diodes are usually placed in PV arrays and they are turned on in mismatched conditions.
However, the operation of bypass diode will cause a number of PV cells to stop deliver power,
\michiko{and it will hence result in a significant loss of power generation.}

@@

PV arrays are hierarchically constructed such that a group of PV cells form a PV module, a group of PV modules form a PV panel, and a group of PV panels form a PV array. 
Power generation of mismatched PV arrays can be recovered by reconfiguring connection of these components. 
Fig.\ref{compare} shows an example of power generations of a PV array with a partial shading. 
We distributed shading cells non-uniformly to a PV array with 3 $\times$  4 PV panels and applied power simulation. 
Before reconfiguration, \michiko{there are} multiple \michiko{peaks in a power - voltage curve with similar power levels,} while, after we reconfigured connection among PV panels, 
\michiko{some peaks exhibit much higher power levels than others and }
%MPPs has reduced and 
% power generation increased by 35\%.
% power generation increased by 35\%.
\zhao{maximum output power increased by 35\%}.

@@

Figure \ref{model} shows an example of a PV array. 
A PV array is a parallel connection of (PV) strings where a string is a series connection of PV panels. 
A PV panel is a series connection of PV modules, and a PV module is a parallel connection of a series of PV cells and a bypass diode. 
A typical commercial PV panel is composed of three PV modules each of which has 12-24 PV cells. 
A PV module can generate power for a given voltage according to its I-V characteristics as shown in Fig.\ref{fig:IV}(a - c). 
The I-V characteristics is affected by irradiance level and physical damage of PV cells. 
\michiko{Figure \ref{fig:IV}(a - c) also show} a typical degradation of a I-V characteristics where generated \michiko{currents are reduced} with some ratio while keeping the voltage range. 
When a PV panel has a partial shade, that is its PV modules have different irradiance levels and hence different I-V characteristics, the PV panels might have multiple peaks (maximum power points, MPPs) in power generation as shown in Fig.\ref{fig:IV}(d).

@@

Step 3 optimizes the number of active modules. 
In Step 3, if the number of active modules exceeds the required number $m$, redundant panels \zhao{are} canceled if exist. 
A panel is \textit{redundant} if the number of active modules is still $m$ or more even if \zhao{the} panel is canceled.
Redundant panels are searched \michiko{for each loss level}. 
Starting with a loss level where the last panel is selected, we check the number of active modules $M_{p}(Q_{n})$ for each panel $p$ 
where $Q_{n}$ is a required current level for the current string.
Redundant panels are selected and canceled from panels with less number of $M_{p}(Q_{n})$ in the same loss level. 
If \michiko{the number of active modules} still exceeds $m$ after canceling,
the same procedure is applied to the previous loss level.
% we will go to the previous loss level and try to cancel panels.
This procedure is repeated until selecting an exactly $m$ active modules or checking all the loss levels.
\michiko{This step accurately finds redundant panels if exist in the following reason. Since the number of active modules in one panel is 0, 1, 2, or 3 \zhao{as assumed in Section \ref{Sec2}} and panels are selected from panels with less active modules in the same loss level, if the number of active modules exceed $m$, the surplus is 1 or 2. That means, the last selected panel has 2 or 3 active modules, and panels with 1 or 2 active modules have already selected if exist.}

@@

\michiko{To evaluate the proposed method, we prepared MPP informations of 100 mismatched PV arrays and applied our algorithm. We also applied an exhaustive searching algorithm for comparison.
MPP information is setup as follows for each PV array. 
Each PV array has 6 - 24  panels and the number of PV panels is randomly determined. 
Three current values are randomly assigned to the three modules in each panel from 3 - 8 current values, where the number of possible current values are also randomly determined for each PV array.
% \zhao{\large \textbf{Is that means: Current value for PV modules in each PV panel are randomly assigned from 3 - 8 current values.}}
The number of strings after reconfiguration is 3 - 6 and it is randomly determined for each PV array.}

@@

\michiko{Table~\ref{result_compare} shows the results of feasibility checking by the proposed algorithm and the exhaustive search.} 
%To evaluate the performance of  proposed algorithm, 
%we compare the result with exhaustive searching algorithm for 100 random shadow distributed PV arrays. For each PV array, 6 - 24 PV panels are connected into 3 - 6 PV strings. For each PV panel, it will has 3 - 8 working current values.
%The computational time required for finding optimal configuration and accuracy of feasibility judgment in the proposed algorithm and exhaustive search algorithm are compared in Table \ref{result_compare}. 
%As shown in Table \ref{result_compare},
% proposed algorithm achieved less computing time compare with exhaustive search algorithm and with high accuracy.  
%from 100 PV arrays, 486 configuration candidates are selected where each candidate is specified with a required current sequence for strings and the number of active modules per string.
Since the exhaustive search checks all the combinations of panel connections for each configuration candidate, it accurately identifies the feasibility of every configuration. % but that takes a lot of time.
\michiko{Though the exhaustive search identified total 327 feasible configurations, the proposed method identified 324 configurations and 3 configurations are misidentified. 
The proposed algorithm had a few false negative cases, but its rate was less than 1\%.
That is, it can correctly identify feasibility for most cases. 
Indeed, the proposed algorithm found at least one candidate configuration as feasible among 4 - 5 candidates for each PV arrays. }
